---
title: "simpleRegress"
author: "MarenaO"
date: "Spring 2022 Semester"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

Chest has an adjusted R-squared value of: 0.7869. It is better than neck and is the second best fit.
```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

Weight has an adjusted R-squared value of: 0.7423. 
Weight seems to be worse than neck, although it is the third best fit.

```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

Age has an adjusted R-squared value of: 0.5023.
Age is way worse than neck but not the worst out of them all.

```{r}
simp <- lm(LENGTH~MONTH,data=bears)
plot(LENGTH~MONTH,data=bears)
abline(simp)
summary.lm(simp)
```

Month has an adjusted R-squared value of: -0.01153.
Month is almost the worst but not quite.

```{r}
simp <- lm(LENGTH~SEX,data=bears)
plot(LENGTH~SEX,data=bears)
abline(simp)
summary.lm(simp)
```

Sex has an adjusted R-squared value of: -0.0084. Out of all the variables, Sex is the worst fit because it has the lowest adjusted r-squared value.

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

Headlen has an adjusted R-squared value of: 0.8434.
Headlength is the best fit.

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

Headwidth has an adjusted R-squared value of: 0.5321. Headwidth seems to not be as good as neck, but it is not the worst.



In order of best to worst: HEADLEN > CHEST >
WEIGHT > HEADWTH > AGE > MONTH > SEX

Neck has an adjusted R-squared value of: 0.7476.
Headlen has an adjusted R-squared value of: 0.8434.
Chest has an adjusted R-squared value of: 0.7869.
Weight has an adjusted R-squared value of: 0.7423.
Headwidth has an adjusted R-squared value of: 0.5321.
Age has an adjusted R-squared value of: 0.5023.
Month has an adjusted R-squared value of: -0.01153.
Sex has an adjusted R-squared value of: -0.0084.

